Housing Default Handovers

### 2024-10-18 minos/validation/housing_handovers.Rmd
updating validation handovers and ncars and ncigs composites

handover_boxplots(raw.dat, base.dat, 'hh_income')
handover_lineplots(raw.dat, base.dat, "hh_income")
```

@@

# net household income. 
handover_boxplots(raw.inc, base.inc, 'net_hh_income')
handover_lineplots(raw.inc, base.inc, "net_hh_income")
inc.spag<-rbind(raw.inc, base.inc)
density_ridges(inc.spag, 'net_hh_income',
               save=TRUE, 
               save.path=save.path)

# rent
handover_boxplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], 'hh_rent')
handover_lineplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], "hh_rent")
density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
               save=TRUE, 
               save.path=save.path)
spaghetti_plot(net.income.spag.sample, 'hh_rent',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(net.income.spag.sample, 'hh_rent',
               save = shall.we.save,
               save.path = save.path)
# mortgage
handover_boxplots(raw.inc[which(raw.inc$hh_mortgage>1 & raw.inc$hh_mortgage<5000), ], base.inc[which(base.inc$hh_mortgage>1 & base.inc$hh_mortgage<5000), ], 'hh_mortgage')
handover_lineplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], "hh_mortgage")
density_ridges(inc.spag[which(inc.spag$hh_mortgage>1 & inc.spag$hh_mortgage<5000), ], 'hh_mortgage',
               save=TRUE, 
               save.path=save.path)
spaghetti_plot(net.income.spag.sample, 'hh_mortgage',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(net.income.spag.sample, "hh_mortgage",
               save = shall.we.save,
               save.path = save.path)
#council tax
handover_boxplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], 'council_tax')
handover_lineplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], "council_tax")
density_ridges(inc.spag[which(inc.spag$council_tax>1), ], 'council_tax',
               save=TRUE, 
               save.path=save.path)
spaghetti_plot(net.income.spag.sample, 'council_tax',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(net.income.spag.sample, "council_tax",
               save = shall.we.save,
               save.path = save.path)

@@

## SF12

@@

raw.sf12 <- raw.dat %>%
  dplyr::select(pidp, time, SF_12_MCS) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12 <- base.dat %>%
  dplyr::select(pidp, time, SF_12_MCS) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
sf12 <- rbind(raw.sf12, base.sf12)

# Now plot
ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_smooth() +
  #geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('SF12')

## Try a version where final_US is limited to only those present from wave 1
# onwards because the sample refreshments are messing with the plot
raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.sf12.2 <- raw.dat %>%
  dplyr::select(pidp, time, SF_12_MCS) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.2 <- base.dat %>%
  dplyr::select(pidp, time, SF_12_MCS) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

sf12.2 <- rbind(raw.sf12.2, base.sf12.2)

# Now plot
ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Mental Wellbeing (SF12 MCS)') +
  xlab('Year') +
  ylab('SF12')

if (shall.we.save) {
  ggsave(filename = 'SF12_wav1.png',
       plot = last_plot(),
       path = save.path)
}

rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
```

@@

```{r}
raw.sf12 <- raw.dat %>%
  select(pidp, age, time, SF_12_MCS)
base.sf12 <- base.dat %>%
  select(pidp, age, time, SF_12_MCS)

sf12.spag <- rbind(raw.sf12, base.sf12)

sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
spaghetti_plot(sf12.spag.sample, 'SF_12_MCS',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_MCS',
               save = shall.we.save,
               save.path = save.path)

density_ridges(sf12.spag, "SF_12_MCS",
               save = T,
               save.path = save.path)

rm(raw.sf12, base.sf12, sf12.spag)
```

@@

## Physical Health

NOTE: At present, physical health is not predicted or transitioned.

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.phealth <- raw.dat %>%
  dplyr::select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth <- base.dat %>%
  dplyr::select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
phealth <- rbind(raw.phealth, base.phealth)

# Now plot
ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Physical Health', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('Average')

## Try a version where final_US is limited to only those present from wave 1
# onwards because the sample refreshments are messing with the plot
raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.phealth2 <- raw.dat %>%
  dplyr::select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth2 <- base.dat %>%
  dplyr::select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

phealth2 <- rbind(raw.phealth2, base.phealth2)

# Now plot
ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Physical Health') +
  xlab('Year') +
  ylab('Average')

if (shall.we.save) {
  ggsave(filename = 'physical_health_wav1.png',
       plot = last_plot(),
       path = save.path)
}

#raw.phealth.check <- raw.dat %>%
#  select(pidp, time, phealth) %>%
#  filter(time > 2009) %>%
#  filter(pidp %in% raw.wave1)

#base.phealth.check <- base.dat %>%
#  select(pidp, time, phealth) %>%
#  filter(time > 2009) %>%
#  filter(pidp %in% raw.wave1)

rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2)
#rm(raw.phealth.check, base.phealth.check)
```

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, phealth)
# base.s <- base.dat %>%
#   select(pidp, age, time, phealth)
#
# spag <- rbind(raw.s, base.s)
#
# spaghetti_plot(spag, 'phealth',
#              save = shall.we.save,
#              save.path = save.path)
#
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, education_state)
# base.s <- base.dat %>%
#   select(pidp, age, time, education_state)
#
# spag <- rbind(raw.s, base.s)
#
# spaghetti_plot(spag, 'education_state',
#                save = shall.we.save,
#                save.path = save.path)
#
# rm(raw.s, base.s, spag)
```

>>>>

handover_boxplots(raw.dat, base.dat, 'hh_income')
handover_lineplots(raw.dat, base.dat, "hh_income")
handover_median_lineplots(raw.dat, base.dat, "hh_income")

@@

# net household income. 
handover_boxplots(raw.inc, base.inc, 'net_hh_income')
handover_lineplots(raw.inc, base.inc, "net_hh_income")
handover_median_lineplots(raw.inc, base.inc, "net_hh_income")

inc.spag<-rbind(raw.inc, base.inc)
density_ridges(inc.spag, 'net_hh_income',
               save=TRUE, 
               save.path=save.path)

# rent
handover_boxplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], 'hh_rent')
handover_lineplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], "hh_rent")
handover_median_lineplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], "hh_rent")

density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
               save=TRUE, 
               save.path=save.path)
spaghetti_plot(net.income.spag.sample, 'hh_rent',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(net.income.spag.sample, 'hh_rent',
               save = shall.we.save,
               save.path = save.path)
# mortgage
handover_boxplots(raw.inc[which(raw.inc$hh_mortgage>1 & raw.inc$hh_mortgage<5000), ], base.inc[which(base.inc$hh_mortgage>1 & base.inc$hh_mortgage<5000), ], 'hh_mortgage')
handover_lineplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], "hh_mortgage")
handover_median_lineplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], "hh_mortgage")

density_ridges(inc.spag[which(inc.spag$hh_mortgage>1 & inc.spag$hh_mortgage<5000), ], 'hh_mortgage',
               save=TRUE, 
               save.path=save.path)
spaghetti_plot(net.income.spag.sample, 'hh_mortgage',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(net.income.spag.sample, "hh_mortgage",
               save = shall.we.save,
               save.path = save.path)
#council tax
handover_boxplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], 'council_tax')
handover_lineplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], "council_tax")
handover_median_lineplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], "council_tax")

density_ridges(inc.spag[which(inc.spag$council_tax>1), ], 'council_tax',
               save=TRUE, 
               save.path=save.path)
spaghetti_plot(net.income.spag.sample, 'council_tax',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(net.income.spag.sample, "council_tax",
               save = shall.we.save,
               save.path = save.path)

@@

## SF12 MCS

@@

raw.sf12_mcs <- raw.dat %>%
  dplyr::select(pidp, time, SF_12_MCS) %>%
  group_by(time) %>%
  summarise(sf12_mcs = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12_mcs <- base.dat %>%
  dplyr::select(pidp, time, SF_12_MCS) %>%
  group_by(time) %>%
  summarise(sf12_mcs = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
sf12_mcs <- rbind(raw.sf12_mcs, base.sf12_mcs)

# Now plot
ggplot(data = sf12_mcs, mapping = aes(x = time, y = sf12_mcs, group = source, colour = source)) +
  geom_smooth() +
  #geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('SF12 MCS')

## Try a version where final_US is limited to only those present from wave 1
# onwards because the sample refreshments are messing with the plot
raw.sf12_mcs.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.sf12_mcs.2 <- raw.dat %>%
  dplyr::select(pidp, time, SF_12_MCS) %>%
  filter(pidp %in% raw.sf12_mcs.wave1) %>%
  group_by(time) %>%
  summarise(sf12_mcs = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12_mcs.2 <- base.dat %>%
  dplyr::select(pidp, time, SF_12_MCS) %>%
  filter(pidp %in% raw.sf12_mcs.wave1) %>%
  group_by(time) %>%
  summarise(sf12_mcs = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

sf12_mcs.2 <- rbind(raw.sf12_mcs.2, base.sf12_mcs.2)

# Now plot
ggplot(data = sf12_mcs.2, mapping = aes(x = time, y = sf12_mcs, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Mental Wellbeing (SF12 MCS)') +
  xlab('Year') +
  ylab('SF12 MCS')

if (shall.we.save) {
  ggsave(filename = 'SF12_MCS_wav1.png',
       plot = last_plot(),
       path = save.path)
}

rm(raw.sf12_mcs, base.sf12_mcs, sf12_mcs, raw.sf12_mcs.wave1, raw.sf12_mcs.2, base.sf12_mcs.2, sf12_mcs.2)
```

@@

```{r}
raw.sf12_mcs <- raw.dat %>%
  select(pidp, age, time, SF_12_MCS)
base.sf12_mcs <- base.dat %>%
  select(pidp, age, time, SF_12_MCS)

sf12_mcs.spag <- rbind(raw.sf12_mcs, base.sf12_mcs)

pidp_sample <- sample(unique(sf12_mcs.spag$pidp), size=100, replace=FALSE)

sf12_mcs.spag.sample <- sf12_mcs.spag[which(sf12_mcs.spag$pidp %in% pidp_sample), ]
spaghetti_plot(sf12_mcs.spag.sample, 'SF_12_MCS',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(sf12_mcs.spag.sample, 'SF_12_MCS',
               save = shall.we.save,
               save.path = save.path)

density_ridges(sf12_mcs.spag, "SF_12_MCS",
               save = T,
               save.path = save.path)

rm(raw.sf12_mcs, base.sf12_mcs, sf12_mcs.spag)
```

## SF12 PCS

```{r}
# sf12 boxplot handovers
handover_boxplots(raw.dat, base.dat, 'SF_12_PCS')
handover_lineplots(raw.dat, base.dat, "SF_12_PCS")

raw.sf12_pcs <- raw.dat %>%
  dplyr::select(pidp, time, SF_12_PCS) %>%
  group_by(time) %>%
  summarise(sf12_pcs = mean(SF_12_PCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12_pcs <- base.dat %>%
  dplyr::select(pidp, time, SF_12_PCS) %>%
  group_by(time) %>%
  summarise(sf12_pcs = mean(SF_12_PCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
sf12_pcs <- rbind(raw.sf12_pcs, base.sf12_pcs)

# Now plot
ggplot(data = sf12_pcs, mapping = aes(x = time, y = sf12_pcs, group = source, colour = source)) +
  geom_smooth() +
  #geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Physical Wellbeing (SF12)', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('SF12 PCS')

## Try a version where final_US is limited to only those present from wave 1
# onwards because the sample refreshments are messing with the plot
raw.sf12_pcs.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.sf12_pcs.2 <- raw.dat %>%
  dplyr::select(pidp, time, SF_12_PCS) %>%
  filter(pidp %in% raw.sf12_pcs.wave1) %>%
  group_by(time) %>%
  summarise(sf12_pcs = mean(SF_12_PCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12_pcs.2 <- base.dat %>%
  dplyr::select(pidp, time, SF_12_PCS) %>%
  filter(pidp %in% raw.sf12_pcs.wave1) %>%
  group_by(time) %>%
  summarise(sf12_pcs = mean(SF_12_PCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

sf12_pcs.2 <- rbind(raw.sf12_pcs.2, base.sf12_pcs.2)

# Now plot
ggplot(data = sf12_pcs.2, mapping = aes(x = time, y = sf12_pcs, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Mental Wellbeing (SF12 MCS)') +
  xlab('Year') +
  ylab('SF12 PCS')

if (shall.we.save) {
  ggsave(filename = 'SF12_PCS_wav1.png',
       plot = last_plot(),
       path = save.path)
}

rm(raw.sf12_pcs, base.sf12_pcs, sf12_pcs, raw.sf12_pcs.wave1, raw.sf12_pcs.2, base.sf12_pcs.2, sf12_pcs.2)
```

```{r}
raw.sf12_pcs <- raw.dat %>%
  select(pidp, age, time, SF_12_PCS)
base.sf12_pcs <- base.dat %>%
  select(pidp, age, time, SF_12_PCS)

sf12_pcs.spag <- rbind(raw.sf12_pcs, base.sf12_pcs)

pidp_sample <- sample(unique(sf12_pcs.spag$pidp), size=100, replace=FALSE)

sf12_pcs.spag.sample <- sf12_pcs.spag[which(sf12_pcs.spag$pidp %in% pidp_sample), ]
spaghetti_plot(sf12_pcs.spag.sample, 'SF_12_PCS',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(sf12_pcs.spag.sample, 'SF_12_PCS',
               save = shall.we.save,
               save.path = save.path)

density_ridges(sf12_pcs.spag, "SF_12_PCS",
               save = T,
               save.path = save.path)

rm(raw.sf12_pcs, base.sf12_pcs, sf12_pcs.spag)
```

@@

<!-- ## Physical Health -->

<!-- NOTE: At present, physical health is not predicted or transitioned. -->

<!-- ```{r} -->
<!-- # first figure out how to plot final_US -->
<!-- # start with hh_income -->
<!-- raw.phealth <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, phealth) %>% -->
<!--   filter(time > 2009) %>% -->
<!--   group_by(time) %>% -->
<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.phealth <- base.dat %>% -->
<!--   dplyr::select(pidp, time, phealth) %>% -->
<!--   filter(time > 2009) %>% -->
<!--   group_by(time) %>% -->
<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- # merge before plot -->
<!-- phealth <- rbind(raw.phealth, base.phealth) -->

<!-- # Now plot -->
<!-- ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Physical Health', subtitle = 'Full Sample') + -->
<!--   xlab('Year') + -->
<!--   ylab('Average') -->

<!-- ## Try a version where final_US is limited to only those present from wave 1 -->
<!-- # onwards because the sample refreshments are messing with the plot -->
<!-- raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009] -->

<!-- raw.phealth2 <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, phealth) %>% -->
<!--   filter(time > 2009) %>% -->
<!--   filter(pidp %in% raw.wave1) %>% -->
<!--   group_by(time) %>% -->
<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.phealth2 <- base.dat %>% -->
<!--   dplyr::select(pidp, time, phealth) %>% -->
<!--   filter(time > 2009) %>% -->
<!--   filter(pidp %in% raw.wave1) %>% -->
<!--   group_by(time) %>% -->
<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- phealth2 <- rbind(raw.phealth2, base.phealth2) -->

<!-- # Now plot -->
<!-- ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Physical Health') + -->
<!--   xlab('Year') + -->
<!--   ylab('Average') -->

<!-- if (shall.we.save) { -->
<!--   ggsave(filename = 'physical_health_wav1.png', -->
<!--        plot = last_plot(), -->
<!--        path = save.path) -->
<!-- } -->

<!-- #raw.phealth.check <- raw.dat %>% -->
<!-- #  select(pidp, time, phealth) %>% -->
<!-- #  filter(time > 2009) %>% -->
<!-- #  filter(pidp %in% raw.wave1) -->

<!-- #base.phealth.check <- base.dat %>% -->
<!-- #  select(pidp, time, phealth) %>% -->
<!-- #  filter(time > 2009) %>% -->
<!-- #  filter(pidp %in% raw.wave1) -->

<!-- rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2) -->
<!-- #rm(raw.phealth.check, base.phealth.check) -->
<!-- ``` -->

<!-- ### Spaghetti -->

<!-- ```{r} -->
<!-- # raw.s <- raw.dat %>% -->
<!-- #   select(pidp, age, time, phealth) -->
<!-- # base.s <- base.dat %>% -->
<!-- #   select(pidp, age, time, phealth) -->
<!-- # -->
<!-- # spag <- rbind(raw.s, base.s) -->
<!-- # -->
<!-- # spaghetti_plot(spag, 'phealth', -->
<!-- #              save = shall.we.save, -->
<!-- #              save.path = save.path) -->
<!-- # -->
<!-- # rm(raw.s, base.s, spag) -->
<!-- ``` -->

## Alcohol (AUDITC)

```{r}
handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)

raw.2020.alc <- raw.dat %>% 
  filter(time == 2020) %>%
  group_by(auditc) %>%
  summarise(n = n()) %>%
  mutate(prop = n / sum(n))

## Physical Activity

```{r}
handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)

raw.2020.phys <- raw.dat %>% 
  filter(time == 2020) %>%
  group_by(active) %>%
  summarise(n = n()) %>%
  mutate(prop = n / sum(n))
```

@@

<!-- ### Spaghetti -->

<!-- ```{r} -->
<!-- # raw.s <- raw.dat %>% -->
<!-- #   select(pidp, age, time, education_state) -->
<!-- # base.s <- base.dat %>% -->
<!-- #   select(pidp, age, time, education_state) -->
<!-- # -->
<!-- # spag <- rbind(raw.s, base.s) -->
<!-- # -->
<!-- # spaghetti_plot(spag, 'education_state', -->
<!-- #                save = shall.we.save, -->
<!-- #                save.path = save.path) -->
<!-- # -->
<!-- # rm(raw.s, base.s, spag) -->
<!-- ``` -->
